Improvement of Korean Morphological Analysis System \\Through Transformer-Based Re-Ranking

### 2023-12-04 contents/draft.tex
table/figure position: h -> ht
Cite BERT

    \begin{table*}[t]
        \caption{Maximum performance of alternative paths as correct answers}
        \label{tab:maximum-performance}
        \centering
        \begin{tabular*}{500pt}{@{\extracolsep\fill}cccD{.}{.}{3}c@{\extracolsep\fill}}
            \toprule
            ~                 & \multicolumn{2}{@{}c@{}}{Written Language Evaluation Set} & \multicolumn{2}{@{}c@{}}{Spoken Language Evaluation Set}                  \\ \cmidrule{2-3} \cmidrule{4-5}
            alternative range & eojeol accuracy & average number of alternative           & \multicolumn{1}{@{}l@{}}{eojeol accuracy} & average number of alternative \\
            \midrule
            no alternative    & 96.36           & 1.0                                     & 92.54                                     & 1.0                           \\
            secondary         & 98.74           & 25.7                                    & 97.27                                     & 12.9                          \\
            tertiary          & 98.96           & 47.8                                    & 97.81                                     & 23.6                          \\
            quarternary       & 99.01           & 69.6                                    & 97.95                                     & 34.2                          \\
            quinary           & 99.02           & 91.1                                    & 98.01                                     & 44.5                          \\
            \bottomrule
        \end{tabular*}
        \begin{tablenotes}
            \footnotesize
            \item\hspace{2mm} * Written Language Evaluation Set: 2,400 sentences each randomized from UCorpus and Everyone's Corpus (4,800 sentences total)
            \item\hspace{2mm} * Spoken Language Evaluation Set: 2,400 sentences each randomized from UCorpus and Everyone's Corpus (4,800 sentences total)
        \end{tablenotes}
    \end{table*}

@@

    \begin{figure*}[h]
        \centerline{\includegraphics[width=1.0\textwidth]{fig;block-v1}}
        \caption{Overall process flow of the proposed method}
        \label{fig:block}
    \end{figure*}

@@

    \begin{table*}[h]
        \centering
        \footnotesize
        \caption{Statistics for the Korean morphological corpus as a whole and for training/test data}
        \label{tab:data-statistics}
        \begin{tabular}{m{20mm}m{14mm}m{10mm}m{12mm}m{10mm}m{10mm}m{12mm}m{10mm}m{10mm}m{12mm}m{10mm}}
            \toprule
            \multirow{2}{*}{Corpus}            & \multirow{2}{*}{Style} & \multicolumn{3}{c}{Raw Data}                 & \multicolumn{3}{c}{Training Data}            & \multicolumn{3}{c}{Test Data}             \\
            \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
            ~                                  & ~                      & sentences & eojeols    & morphs\newline/sent & sentences & eojeols    & morphs\newline/sent & sentences & eojeols & morphs\newline/sent \\
            \midrule
            Sejong Corpus                      & written                & 854,475   & 10,052,869 & 26.8                & 194,822   & 2,681,582  & 31.0                & 49,922    & 678,578 & 30.6                \\
            \midrule
            \multirow{3}{*}{UCorpus}           & written                & 5,456,101 & 62,462,158 & 25.1                & 4,998,560 & 57,393,332 & 25.4                & 53,003    & 598,413 & 25.0                \\
            ~                                  & semi-spoken            & 393,770   & 3,401,444  & 18.4                & 334,061   & 2,960,146  & 19.4                & 38,960    & 332,285 & 18.6                \\
            ~                                  & spoken                 & 627,380   & 2,819,427  & 10.9                & 429,215   & 2,295,940  & 13.0                & 62,399    & 279,545 & 11.1                \\
            \midrule
            \multirow{2}{*}{Everyone's Corpus} & written                & 150,082   & 2,000,213  & 30.4                & 129,352   & 1,713,367  & 30.5                & 14,442    & 191,223 & 30.5                \\
            ~                                  & spoken                 & 221,371   & 1,006,287  & 8.7                 & 137,869   & 714,021    & 10.5                & 19,789    & 85,316  & 8.6                 \\
            \bottomrule
        \end{tabular}
    \end{table*}

@@

    \begin{figure*}[h]
        \centerline{\includegraphics[width=0.9\textwidth]{fig;sample-v3}}
        \caption{Transformation of a single sentence in the Korean morpheme-tagged corpus into a single training sample}
        \label{fig:sample}
    \end{figure*}

@@

    \begin{figure*}[h]
        \centerline{\includegraphics[width=1.0\textwidth]{fig;lattice-v3}}
        \caption{Example of lattice construction and decoding result and secondary path generation}
        \label{fig:lattice}
    \end{figure*}

@@

    \begin{figure*}[h]
        \centerline{\includegraphics[width=0.9\textwidth]{fig;ranking-v2}}
        \caption{Two-stage re-ranking model for Korean morphological analysis}
        \label{fig:ranking}
    \end{figure*}

@@

    Bidirectional Encoder Representations from Transformers (BERT) models have transformed numerous natural language processing tasks by comprehending the contextual nuances in which words appear in text.
    In our study, we aim to harness the capabilities of BERT to reorder the generated secondary paths.
    We assigned scores related to morphological analysis performance to the generated secondary paths and utilized them for fine-tuning a pre-trained BERT model specifically designed for Korean, enriched with a substantial amount of Korean text.
    After preliminary testing with various scoring methods on a modest scale, we found that using scores based on the degree of error, rather than accuracy-based scores, effectively widens the gap between correct and incorrect answers.

@@

    \begin{table*}[h]
        \caption{Performance comparison between morphological analysis systems without re-ranking}
        \label{tab:performance-without-reranking}
        \begin{tabular*}{500pt}{@{\extracolsep\fill}c|cccccc@{\extracolsep\fill}}
            \toprule
            \multirow{2}{*}{System}                & \multicolumn{2}{c}{Sejong}                                & \multicolumn{2}{c}{UCorpus (written)}                     & \multicolumn{2}{c}{Everyone's Corpus (written)}           \\
            \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
            ~                                      & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
            \midrule
            \hspace{2mm}MeCab-ko                   & 89.17                      & 93.06                        & 87.88                      & 92.32                        & 87.77                      & 92.05                        \\
            \hspace{2mm}Syllable-based (written)   & 91.95                      & 95.16                        & \textbf{96.84}             & \textbf{97.97}               & \textbf{98.00}             & \textbf{98.82}               \\
            \hspace{2mm}Dictionary-based (written) & 90.99                      & 94.58                        & 96.33                      & 97.74                        & 96.85                      & 98.14                        \\
            \hspace{2mm}Dictionary-based (Sejong)  & \textbf{95.23}             & \textbf{97.08}               & 90.18                      & 94.19                        & 91.30                      & 94.79                        \\
            \toprule
            \multirow{2}{*}{System}                & \multicolumn{2}{c}{UCorpus (semi-spoken)}                 & \multicolumn{2}{c}{UCorpus (spoken)}                      & \multicolumn{2}{c}{Everyone's Corpus (spoken)}            \\
            \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
            ~                                      & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
            \midrule
            \hspace{2mm}MeCab-ko                   & 86.85                      & 91.38                        & 81.75                      & 87.90                        & 85.28                      & 89.52                        \\
            \hspace{2mm}Syllable-based (spoken)    & \textbf{96.56}             & \textbf{97.65}               & \textbf{94.89}             & \textbf{96.76}               & \textbf{95.14}             & \textbf{96.82}               \\
            \hspace{2mm}Dictionary-based (spoken)  & 94.98                      & 96.65                        & 93.02                      & 95.71                        & 92.47                      & 94.83                        \\
            \bottomrule
        \end{tabular*}
    \end{table*}

    \begin{table*}[h]
        \caption{Performance comparison between morphological analysis systems with Two-stage re-ranking}
        \label{tab:performance-with-reranking}
        \begin{tabular*}{500pt}{@{\extracolsep\fill}c|cccccc@{\extracolsep\fill}}
            \toprule
            \multirow{2}{*}{System}                       & \multicolumn{2}{c}{Sejong}                                & \multicolumn{2}{c}{UC+EC (written)}                       & \multicolumn{2}{c}{UC+EC (spoken)}                        \\
            \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
            ~                                             & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
            \midrule
            \hspace{2mm}MeCab-ko                          & 89.17                      & 93.06                        & 87.83                      & 92.19                        & 84.62                      & 89.60                        \\
            \hspace{2mm}Syllable-based                    & 91.95                      & 95.16                        & 97.42                      & 98.39                        & 95.53                      & \textbf{97.08}               \\
            \hspace{2mm}Dictionary-based (without rerank) & 95.23                      & 97.08                        & 96.59                      & 97.94                        & 93.49                      & 95.73                        \\
            \hspace{2mm}Dictionary-based (1-stage rerank) & 96.63                      & 97.84                        & 97.50                      & 98.44                        & 94.77                      & 96.62                        \\
            \hspace{2mm}Dictionary-based (2-stage rerank) & \textbf{96.87}             & \textbf{98.01}               & \textbf{97.75}             & \textbf{98.60}               & \textbf{95.56}             & \textbf{97.08}               \\
            \bottomrule
        \end{tabular*}
    \end{table*}

@@

    \begin{table}[h]
        \centering
        \footnotesize
        \caption{Training Options and Software Information for Re-ranking Model}
        \label{tab:training-options}
        \begin{tabular}{|p{24mm}|p{25mm}|p{25mm}|}
            \hline
            ~                     & \textbf{First-Stage}                & \textbf{Second-Stage}                                        \\ \hline
            Input Type            & Only Morphological Analysis Results & First Morphological Analysis Results and Original Input Sentences \\ \hline
            Max Sequence Length   & 384                                 & 512                                                               \\ \hline
            Minibatch Size        & 120                                 & 40                                                                \\ \hline
            Training Epochs       & 5                                   & 7                                                                 \\ \hline
            Devices Used          & \multicolumn{2}{l|}{4 GPUs}                                                                             \\ \hline
            Distribution Strategy & \multicolumn{2}{l|}{ddp}                                                                                \\ \hline
            FP Precision          & \multicolumn{2}{l|}{16-bit}                                                                             \\ \hline
            Learning Rate         & \multicolumn{2}{l|}{$2 \times 10^{-5}$}                                                                 \\ \hline
            LR Scheduler          & \multicolumn{2}{l|}{ExponentialLR (gamma=0.9)}                                                          \\ \hline
            Optimizer Type        & \multicolumn{2}{l|}{AdamW}                                                                              \\ \hline
            PyTorch               & \multicolumn{2}{l|}{version 2.0.1}                                                                      \\ \hline
            PyTorch Lightning     & \multicolumn{2}{l|}{version 2.0.6}                                                                      \\ \hline
            Transformers          & \multicolumn{2}{l|}{version 4.31.0}                                                                     \\ \hline
        \end{tabular}
    \end{table}

@@

    \begin{table*}[]
        \caption{Comparison of performance differences with previous studies}
        \label{tab:differences-with-previous-studies}
        \begin{tabular*}{500pt}{@{\extracolsep\fill}ccc|cc@{\extracolsep\fill}}
            \toprule
            \multirow{2}{*}{Study}                & \multirow{2}{*}{Model}                          & \multirow{2}{*}{Data (train, test)}         & \multicolumn{2}{c}{Performance}                           \\
            \cmidrule{4-5}
            ~                                     & ~                                               & ~                                           & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
            \midrule
            Na, 2015~\cite{NaSH2015}              & CRF++, Lattice-based HMM                        & Sejong 200k, 50k sentences                  & 95.22                      & 97.21                        \\
            Lee et al., 2016~\cite{LeeCH2016}     & Structural SVM                                  & Sejong 666k, 74k eojeols                    & 96.41                      & -                            \\
            Li et al., 2017~\cite{Li2017}         & Seq2seq (GRU-based)                             & Sejong 90k, 10k sentences                   & 95.33                      & 97.15                        \\
            Na and Kim, 2018~\cite{NaSH2018}      & Lattice + HMM                                   & Sejong 200k, 50k sentences                  & 96.35                      & 97.74                        \\
            Min et al., 2019~\cite{MinJW2019}     & Seq2seq (Transition-based)                      & Sejong 200k, 50k sentences                  & 96.34                      & 97.68                        \\
            Song and Park, 2019~\cite{SongHJ2019} & Seq2seq (BiLSTM-based)                          & Sejong 200k, 50k sentences                  & 95.68                      & 97.43                        \\
            Youn et al, 2021~\cite{YounJY2021}    & Seq2seq (BERT-based)                            & Sejong 675k, 75k sentences                  & 95.99                      & 97.94                        \\
            Shin et al, 2023~\cite{ShinHJ2023}    & Transformer(Encoder) + BiLSTM                   & Sejong 769k, 87k sentences                  & 96.12                      & 97.74                        \\
            \midrule
            Proposed (without rerank)             & \multirow{3}{*}{Lattice + Transformer(Encoder)} & \multirow{3}{*}{Sejong 194k, 10k sentences} & 95.23                      & 97.08                        \\
            Proposed (1-stage rerank)             & ~                                               & ~                                           & 96.63                      & 97.84                        \\
            Proposed (2-stage rerank)             & ~                                               & ~                                           & \textbf{96.87}             & \textbf{98.01}               \\
            \bottomrule
        \end{tabular*}
    \end{table*}

@@

    \begin{table}[h!]

>>>>

    \begin{table*}[ht]
        \caption{Maximum performance of alternative paths as correct answers}
        \label{tab:maximum-performance}
        \centering
        \begin{tabular*}{500pt}{@{\extracolsep\fill}cccD{.}{.}{3}c@{\extracolsep\fill}}
            \toprule
            ~                 & \multicolumn{2}{@{}c@{}}{Written Language Evaluation Set} & \multicolumn{2}{@{}c@{}}{Spoken Language Evaluation Set}                  \\ \cmidrule{2-3} \cmidrule{4-5}
            alternative range & eojeol accuracy & average number of alternative           & \multicolumn{1}{@{}l@{}}{eojeol accuracy} & average number of alternative \\
            \midrule
            no alternative    & 96.36           & 1.0                                     & 92.54                                     & 1.0                           \\
            secondary         & 98.74           & 25.7                                    & 97.27                                     & 12.9                          \\
            tertiary          & 98.96           & 47.8                                    & 97.81                                     & 23.6                          \\
            quarternary       & 99.01           & 69.6                                    & 97.95                                     & 34.2                          \\
            quinary           & 99.02           & 91.1                                    & 98.01                                     & 44.5                          \\
            \bottomrule
        \end{tabular*}
        \begin{tablenotes}
            \footnotesize
            \item\hspace{2mm} * Written Language Evaluation Set: 2,400 sentences each randomized from UCorpus and Everyone's Corpus (4,800 sentences total)
            \item\hspace{2mm} * Spoken Language Evaluation Set: 2,400 sentences each randomized from UCorpus and Everyone's Corpus (4,800 sentences total)
        \end{tablenotes}
    \end{table*}

@@

    \begin{figure*}[ht]
        \centerline{\includegraphics[width=1.0\textwidth]{fig;block-v1}}
        \caption{Overall process flow of the proposed method}
        \label{fig:block}
    \end{figure*}

@@

    \begin{table*}[ht]
        \centering
        \footnotesize
        \caption{Statistics for the Korean morphological corpus as a whole and for training/test data}
        \label{tab:data-statistics}
        \begin{tabular}{m{20mm}m{14mm}m{10mm}m{12mm}m{10mm}m{10mm}m{12mm}m{10mm}m{10mm}m{12mm}m{10mm}}
            \toprule
            \multirow{2}{*}{Corpus}            & \multirow{2}{*}{Style} & \multicolumn{3}{c}{Raw Data}                 & \multicolumn{3}{c}{Training Data}            & \multicolumn{3}{c}{Test Data}             \\
            \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
            ~                                  & ~                      & sentences & eojeols    & morphs\newline/sent & sentences & eojeols    & morphs\newline/sent & sentences & eojeols & morphs\newline/sent \\
            \midrule
            Sejong Corpus                      & written                & 854,475   & 10,052,869 & 26.8                & 194,822   & 2,681,582  & 31.0                & 49,922    & 678,578 & 30.6                \\
            \midrule
            \multirow{3}{*}{UCorpus}           & written                & 5,456,101 & 62,462,158 & 25.1                & 4,998,560 & 57,393,332 & 25.4                & 53,003    & 598,413 & 25.0                \\
            ~                                  & semi-spoken            & 393,770   & 3,401,444  & 18.4                & 334,061   & 2,960,146  & 19.4                & 38,960    & 332,285 & 18.6                \\
            ~                                  & spoken                 & 627,380   & 2,819,427  & 10.9                & 429,215   & 2,295,940  & 13.0                & 62,399    & 279,545 & 11.1                \\
            \midrule
            \multirow{2}{*}{Everyone's Corpus} & written                & 150,082   & 2,000,213  & 30.4                & 129,352   & 1,713,367  & 30.5                & 14,442    & 191,223 & 30.5                \\
            ~                                  & spoken                 & 221,371   & 1,006,287  & 8.7                 & 137,869   & 714,021    & 10.5                & 19,789    & 85,316  & 8.6                 \\
            \bottomrule
        \end{tabular}
    \end{table*}

@@

    \begin{figure*}[ht]
        \centerline{\includegraphics[width=0.9\textwidth]{fig;sample-v3}}
        \caption{Transformation of a single sentence in the Korean morpheme-tagged corpus into a single training sample}
        \label{fig:sample}
    \end{figure*}

@@

    \begin{figure*}[ht]
        \centerline{\includegraphics[width=1.0\textwidth]{fig;lattice-v3}}
        \caption{Example of lattice construction and decoding result and secondary path generation}
        \label{fig:lattice}
    \end{figure*}

@@

    \begin{figure*}[ht]
        \centerline{\includegraphics[width=0.9\textwidth]{fig;ranking-v2}}
        \caption{Two-stage re-ranking model for Korean morphological analysis}
        \label{fig:ranking}
    \end{figure*}

@@

    Bidirectional Encoder Representations from Transformers (BERT) models~\cite{Devlin2019} have transformed numerous natural language processing tasks by comprehending the contextual nuances in which words appear in text.
    In our study, we aim to harness the capabilities of BERT to reorder the generated secondary paths.
    We assigned scores related to morphological analysis performance to the generated secondary paths and utilized them for fine-tuning a pre-trained BERT model specifically designed for Korean, enriched with a substantial amount of Korean text.
    After preliminary testing with various scoring methods on a modest scale, we found that using scores based on the degree of error, rather than accuracy-based scores, effectively widens the gap between correct and incorrect answers.

@@

    \begin{table*}[ht]
        \caption{Performance comparison between morphological analysis systems without re-ranking}
        \label{tab:performance-without-reranking}
        \begin{tabular*}{500pt}{@{\extracolsep\fill}c|cccccc@{\extracolsep\fill}}
            \toprule
            \multirow{2}{*}{System}                & \multicolumn{2}{c}{Sejong}                                & \multicolumn{2}{c}{UCorpus (written)}                     & \multicolumn{2}{c}{Everyone's Corpus (written)}           \\
            \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
            ~                                      & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
            \midrule
            \hspace{2mm}MeCab-ko                   & 89.17                      & 93.06                        & 87.88                      & 92.32                        & 87.77                      & 92.05                        \\
            \hspace{2mm}Syllable-based (written)   & 91.95                      & 95.16                        & \textbf{96.84}             & \textbf{97.97}               & \textbf{98.00}             & \textbf{98.82}               \\
            \hspace{2mm}Dictionary-based (written) & 90.99                      & 94.58                        & 96.33                      & 97.74                        & 96.85                      & 98.14                        \\
            \hspace{2mm}Dictionary-based (Sejong)  & \textbf{95.23}             & \textbf{97.08}               & 90.18                      & 94.19                        & 91.30                      & 94.79                        \\
            \toprule
            \multirow{2}{*}{System}                & \multicolumn{2}{c}{UCorpus (semi-spoken)}                 & \multicolumn{2}{c}{UCorpus (spoken)}                      & \multicolumn{2}{c}{Everyone's Corpus (spoken)}            \\
            \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
            ~                                      & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
            \midrule
            \hspace{2mm}MeCab-ko                   & 86.85                      & 91.38                        & 81.75                      & 87.90                        & 85.28                      & 89.52                        \\
            \hspace{2mm}Syllable-based (spoken)    & \textbf{96.56}             & \textbf{97.65}               & \textbf{94.89}             & \textbf{96.76}               & \textbf{95.14}             & \textbf{96.82}               \\
            \hspace{2mm}Dictionary-based (spoken)  & 94.98                      & 96.65                        & 93.02                      & 95.71                        & 92.47                      & 94.83                        \\
            \bottomrule
        \end{tabular*}
    \end{table*}

    \begin{table*}[ht]
        \caption{Performance comparison between morphological analysis systems with Two-stage re-ranking}
        \label{tab:performance-with-reranking}
        \begin{tabular*}{500pt}{@{\extracolsep\fill}c|cccccc@{\extracolsep\fill}}
            \toprule
            \multirow{2}{*}{System}                       & \multicolumn{2}{c}{Sejong}                                & \multicolumn{2}{c}{UC+EC (written)}                       & \multicolumn{2}{c}{UC+EC (spoken)}                        \\
            \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
            ~                                             & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
            \midrule
            \hspace{2mm}MeCab-ko                          & 89.17                      & 93.06                        & 87.83                      & 92.19                        & 84.62                      & 89.60                        \\
            \hspace{2mm}Syllable-based                    & 91.95                      & 95.16                        & 97.42                      & 98.39                        & 95.53                      & \textbf{97.08}               \\
            \hspace{2mm}Dictionary-based (without rerank) & 95.23                      & 97.08                        & 96.59                      & 97.94                        & 93.49                      & 95.73                        \\
            \hspace{2mm}Dictionary-based (1-stage rerank) & 96.63                      & 97.84                        & 97.50                      & 98.44                        & 94.77                      & 96.62                        \\
            \hspace{2mm}Dictionary-based (2-stage rerank) & \textbf{96.87}             & \textbf{98.01}               & \textbf{97.75}             & \textbf{98.60}               & \textbf{95.56}             & \textbf{97.08}               \\
            \bottomrule
        \end{tabular*}
    \end{table*}

@@

    \begin{table}[ht]
        \centering
        \footnotesize
        \caption{Training Options and Software Information for Re-ranking Model}
        \label{tab:training-options}
        \begin{tabular}{|p{24mm}|p{25mm}|p{25mm}|}
            \hline
            ~                     & \textbf{First-Stage}                & \textbf{Second-Stage}                                        \\ \hline
            Input Type            & Only Morphological Analysis Results & First Morphological Analysis Results and Original Input Sentences \\ \hline
            Max Sequence Length   & 384                                 & 512                                                               \\ \hline
            Minibatch Size        & 120                                 & 40                                                                \\ \hline
            Training Epochs       & 5                                   & 7                                                                 \\ \hline
            Devices Used          & \multicolumn{2}{l|}{4 GPUs}                                                                             \\ \hline
            Distribution Strategy & \multicolumn{2}{l|}{ddp}                                                                                \\ \hline
            FP Precision          & \multicolumn{2}{l|}{16-bit}                                                                             \\ \hline
            Learning Rate         & \multicolumn{2}{l|}{$2 \times 10^{-5}$}                                                                 \\ \hline
            LR Scheduler          & \multicolumn{2}{l|}{ExponentialLR (gamma=0.9)}                                                          \\ \hline
            Optimizer Type        & \multicolumn{2}{l|}{AdamW}                                                                              \\ \hline
            PyTorch               & \multicolumn{2}{l|}{version 2.0.1}                                                                      \\ \hline
            PyTorch Lightning     & \multicolumn{2}{l|}{version 2.0.6}                                                                      \\ \hline
            Transformers          & \multicolumn{2}{l|}{version 4.31.0}                                                                     \\ \hline
        \end{tabular}
    \end{table}

@@

    \begin{table*}[ht]
        \caption{Comparison of performance differences with previous studies}
        \label{tab:differences-with-previous-studies}
        \begin{tabular*}{500pt}{@{\extracolsep\fill}ccc|cc@{\extracolsep\fill}}
            \toprule
            \multirow{2}{*}{Study}                & \multirow{2}{*}{Model}                          & \multirow{2}{*}{Data (train, test)}         & \multicolumn{2}{c}{Performance}                           \\
            \cmidrule{4-5}
            ~                                     & ~                                               & ~                                           & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
            \midrule
            Na, 2015~\cite{NaSH2015}              & CRF++, Lattice-based HMM                        & Sejong 200k, 50k sentences                  & 95.22                      & 97.21                        \\
            Lee et al., 2016~\cite{LeeCH2016}     & Structural SVM                                  & Sejong 666k, 74k eojeols                    & 96.41                      & -                            \\
            Li et al., 2017~\cite{Li2017}         & Seq2seq (GRU-based)                             & Sejong 90k, 10k sentences                   & 95.33                      & 97.15                        \\
            Na and Kim, 2018~\cite{NaSH2018}      & Lattice + HMM                                   & Sejong 200k, 50k sentences                  & 96.35                      & 97.74                        \\
            Min et al., 2019~\cite{MinJW2019}     & Seq2seq (Transition-based)                      & Sejong 200k, 50k sentences                  & 96.34                      & 97.68                        \\
            Song and Park, 2019~\cite{SongHJ2019} & Seq2seq (BiLSTM-based)                          & Sejong 200k, 50k sentences                  & 95.68                      & 97.43                        \\
            Youn et al, 2021~\cite{YounJY2021}    & Seq2seq (BERT-based)                            & Sejong 675k, 75k sentences                  & 95.99                      & 97.94                        \\
            Shin et al, 2023~\cite{ShinHJ2023}    & Transformer(Encoder) + BiLSTM                   & Sejong 769k, 87k sentences                  & 96.12                      & 97.74                        \\
            \midrule
            Proposed (without rerank)             & \multirow{3}{*}{Lattice + Transformer(Encoder)} & \multirow{3}{*}{Sejong 194k, 10k sentences} & 95.23                      & 97.08                        \\
            Proposed (1-stage rerank)             & ~                                               & ~                                           & 96.63                      & 97.84                        \\
            Proposed (2-stage rerank)             & ~                                               & ~                                           & \textbf{96.87}             & \textbf{98.01}               \\
            \bottomrule
        \end{tabular*}
    \end{table*}

@@

    \begin{table}[ht]
